A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/conclusion_RECOMB.tex
conclusion

In this article we presented a new 
 pseudo-energetic model taking into account the energetic contribution 
of the stacked base pairs and the isostericity of all base pairs. 
We also showed that a secondary structure allows to efficiently
explore the mutational landscape and that we can benefit from the
 conserved consensus secondary structures  information
to identify and fix sequencing errors.
By combining the pseudo-energetic model and the 
mutational landscape exploration we are able  to efficiently 
correct randomly mutated 5s rRNA sequences. 
As presented in Sec.~\ref{sec:results},
we observe that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.

>>>>

In this article we presented a new 
 pseudo-energetic model taking into account the energetic contribution 
of the stacked base pairs and the isostericity of all base pairs. 
We also showed that a secondary structure allows to efficiently
explore the mutational landscape and that we can benefit from the
 conserved consensus secondary structures  information
to identify and fix sequencing errors.

By combining those two approaches, the pseudo-energetic model and the 
mutational landscape exploration, we are able  to efficiently 
correct randomly mutated 5s rRNA sequences. 
As presented in Sec.~\ref{sec:results},
we observe that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.
